Online Verification of Commutativity

### 2020-07-28 acmPaper/paper.tex
Add fncylab to use labelformat
Murota implementation:
Added a stub for evaluation

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{inputSet S, codomain = Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ Rs}{
        smallerPairs $\gets$ \{\}\;
        \For{candidateBilinking $\in$ Rs}{
            \If{$\exists$ path from bilinking.source to candidateBilinking.source
            and
            $\exists$ path from candidateBilinking.sink to bilinking.sink}{
                \tcc{Check if there's a linear dependence between the bilinking and smallerPairs.
                    Vectorize(pair) returns a vector with a dimension for each edge in the graph,
                    with a 1 if pair includes that edge and 0 if it doesn't.}    
                matrix $\gets$ [vectorize(pair) for pair in smallerPair]\;
                matrix $\gets$ matrix+[vectorize(bilinking)]\;
                \If{determinant(matrix)\%2==0}{
                    output.add(bilinking)
                }
            }
        }
    }
    \KwRet{output}
}

@@

Averaging over evaluation for the first 30 days of 2020, building and verifying a diagram to completion (inclusive of the time required by network calls) took 243$\pm$19 seconds using algorithm ~\ref{algo_online_minimal}, and in 133$\pm$13 seconds with algorithm ~\ref{algo_online_polynomial}. 
Computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.
More information about implementation can be found in the evaluation section.

\section{Evaluation}

>>>>

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{inputSet S, codomain = Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ S}{
        smallerPairs $\gets$ \{\}\;
        \For{candidateBilinking $\in$ Rs}{
            \If{$\exists$ path from bilinking.source to candidateBilinking.source
            and
            $\exists$ path from candidateBilinking.sink to bilinking.sink}{
                \tcc{Check if there's a linear dependence between the bilinking and smallerPairs.
                    Vectorize(pair) returns a vector with a dimension for each edge in the graph,
                    with a 1 if pair includes that edge and 0 if it doesn't.}    
                matrix $\gets$ [vectorize(pair) for pair in smallerPair]\;
                matrix $\gets$ matrix+[vectorize(bilinking)]\;
                \If{determinant(matrix)\%2==0}{
                    output.add(bilinking)
                }
            }
        }
    }
    \KwRet{output}
}

@@

Averaging over evaluation for the first 30 days of 2020, building and verifying a diagram to completion (inclusive of the time required by network calls) took 243$\pm$19 seconds using algorithm ~\ref{algo_online_minimal}, and in 133$\pm$13 seconds with algorithm ~\ref{algo_online_polynomial}.

\section{Evaluation}
We compare performance of the following path checking algorithms: (1) naive baseline (2) less naive, two-flip baseline (3) batch baseline (4) algorithm ~\ref{algo_online_polynomial}, and (5) algorithm ~\ref{algo_online_minimal}.
The two aspects we look at are time for response and size of response set (smaller sets -- tighter output results -- would mean less calls to the oracle).
We use randomly generated graphs for benchmarking, and vary their size.
All computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.

The naive baseline performs poorly, taking well over a thousand seconds for even small graphs of 10 nodes.
The batch algorithm brings timing down to seconds. Algorithm ~\ref{algo_online_polynomial} performs only slightly better.
Surprisingly, the optimal set algorithm cuts time cost by several orders of magnitude.
All implementations are sensitive to density, performing better when density is very low or very high.

%TODO add figures

\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds taken for ten nodes, density close to 0.5 \\
    \hline
    Naive baseline & 1,500 \\
    Batch algorithm & 1.4 \\
    algorithm ~\ref{algo_online_polynomial} & 1.2 \\
    algorithm ~\ref{algo_online_minimal} & 0.0006 \\
    \hline
\end{tabular}
